---
title: "CodeBook.Rmd"
author: "Anish"
date: "July 26, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Download the dataset

Dataset downloaded and extracted under the folder called UCI HAR Dataset

## Assigned each data to variables

```{r UCI}
features <- features.txt # The features selected for this database come from the accelerometer and gyroscope 3-axial raw signals.
activities <- activity_labels.txt # List of activities performed when the corresponding measurements were taken and its codes (labels)
subject_test <- test/subject_test.txt # contains test data of volunteer test subjects being observed
x_test <- test/X_test.txt # contains recorded features test data
y_test <- test/y_test.txt # contains test data of activity code labels
subject_train <- test/subject_train.txt # contains train data of volunteer subjects being observed
x_train <- test/X_train.txt # contains recorded features train data
y_train <- test/y_train.txt # contains train data of activities’code labels

```
## Merges the training and the test sets to create one data set

```{r MERGE}
X <- rbind(x_train, x_test) # X is created by merging x_train and x_test using rbind() function
Y <- rbind(y_train, y_test) # Y is created by merging y_train and y_test using rbind() function
Subject <- rbind(subject_train, subject_test) # Subject is created by merging subject_train and subject_test using rbind() function
Merged_Data <- cbind(Subject, Y, X) # Merged_Data is created by merging Subject, Y and X using cbind() function
```
## Extracts only the measurements on the mean and standard deviation for each measurement

TidyData with (10299 rows, 88 columns) is created by subsetting Merged_Data, selecting only columns: subject, code and the measurements on the mean and standard deviation (std) for each measurement
```{r TIDY_SET}
TidyData <- select(Merged_Data, subject, code, contains("mean"), contains("std"))
```
## Uses descriptive activity names to name the activities in the data set

Entire numbers in code column of the TidyData replaced with corresponding activity taken from second column of the activities variable.
Code column in TidyData renamed into activities
All Acc in column’s name replaced by Accelerometer
All Gyro in column’s name replaced by Gyroscope
All BodyBody in column’s name replaced by Body
All Mag in column’s name replaced by Magnitude
All start with character f in column’s name replaced by Frequency
All start with character t in column’s name replaced by Time

## Final Independent tidy data set with the average of each variable for each activity and each subject created
FinalData (180 rows, 88 columns) is created by sumarizing TidyData taking the means of each variable for each activity and each subject, after groupped by subject and activity.
```{r SUMMARISE}
FinalData <- TidyData %>%
  group_by(subject, activity) %>%
  summarise_all(funs(mean))

```
